---
title: "Data 607 - Project 2"
author: "Shamecca Marshall"
date: "2023-10-08"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal of this assignment is to give you practice in preparing different datasets for downstream
analysis work.
Your task is to:
(1) Choose any three of the “wide” datasets identified in the Week 5 Discussion items. (You may
use your own dataset; please don’t use my Sample Post dataset, since that was used in your
Week 6 assignment!) For each of the three chosen datasets:
• Create a .CSV file (or optionally, a MySQL database!) that includes all of the information
included in the dataset. You’re encouraged to use a “wide” structure similar to how the
information appears in the discussion item, so that you can practice tidying and
transformations as described below.
• Read the information from your .CSV file into R, and use tidyr and dplyr as needed to tidy
and transform your data. [Most of your grade will be based on this step!]
• Perform the analysis requested in the discussion item.
• Your code should be in an R Markdown file, posted to rpubs.com, and should include
narrative descriptions of your data cleanup work, analysis, and conclusions. 

```{r include=FALSE}
library(tidyverse)
library(dplyr)
library(tidyr)
library(ggplot2)
```

## Load CVS file from github
```{r}
theUrl <- "https://raw.githubusercontent.com/Meccamarshall/Data607/main/unemployment%20rate.csv"

df <- read.csv(file = theUrl, header = TRUE, sep = ",")
head(df)
```

# Viewing column
```{r}
colnames(df)
```
# Renaming Column
```{r}
library(tidyr)
df2<-rename(df,State=State.Area, Unemployment_percentage=Percent.....of.Labor.Force.Unemployed.in.State.Area)
head(df2)
```

# Analysis of data will be performed by creating visualization of monthly unemployment rates of a single state for time from 1976-2020 The state chosen is California. Based on the chart, California has had a unemployment rate hovering between 3.8% and 16.1% between 1976 and 2020 The highest unemployment time for California was during the months of April 2020 and August 2020 during covid-19.
```{r}
library(ggplot2)
California<-subset(df2,State=="California")
ggplot(California, aes(x=California$Year, y=California$Unemployment_percentage, fill=California$Month)) + geom_line(color = "hotpink")
```



