---
title: "Data 607 - Project 2"
author: "Shamecca Marshall"
date: "2023-10-08"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal of this assignment is to give you practice in preparing different datasets for downstream
analysis work.
Your task is to:
(1) Choose any three of the “wide” datasets identified in the Week 5 Discussion items. (You may
use your own dataset; please don’t use my Sample Post dataset, since that was used in your
Week 6 assignment!) For each of the three chosen datasets:
• Create a .CSV file (or optionally, a MySQL database!) that includes all of the information
included in the dataset. You’re encouraged to use a “wide” structure similar to how the
information appears in the discussion item, so that you can practice tidying and
transformations as described below.
• Read the information from your .CSV file into R, and use tidyr and dplyr as needed to tidy
and transform your data. [Most of your grade will be based on this step!]
• Perform the analysis requested in the discussion item.
• Your code should be in an R Markdown file, posted to rpubs.com, and should include
narrative descriptions of your data cleanup work, analysis, and conclusions. 

```{r include=FALSE}
library(tidyverse)
library(dplyr)
library(tidyr)
library(ggplot2)
library(gapminder)
library(reshape2)
library(ggpubr)
library(usmap)
library(lubridate)
library(kableExtra)
```

### DATASET 1

# Loading Data from Github
This data was found on Kaggle.com
```{r}
candy_df <- read.csv('https://raw.githubusercontent.com/Meccamarshall/Data607/main/Project%202/Candydata.csv', stringsAsFactors = FALSE)
head(candy_df)
```

### Cleaning the Data
```{r}
candy1 <- candy_df %>% select(starts_with('Q2'), starts_with('Q6')) %>%
  rename(gender = Q2..GENDER) %>%
  gather('candy_name','preference',2:50) %>% 
  mutate(candy_name= str_replace(candy_name, 'Q6\\.{3}(.+)','\\1'),
         preference = str_trim(preference, side = 'both')) %>%
  filter(!preference == '' & (gender == 'Male' | gender == 'Female')) %>%
  group_by(gender,candy_name,preference) %>%
  tally() %>%
  spread(preference,n)
candy1
```

### Creating Visuals and Analyzing Data
Viewing the top five candies that are "meh" to both guys and girls.
```{r}
plot1=ggplot(arrange(filter(candy1, gender == 'Female'),desc(MEH))[1:5,], aes(x=reorder(candy_name, MEH), y = MEH, fill = MEH))+
  geom_bar(stat = 'identity')+
  coord_flip()+
  geom_text(aes(label=MEH),vjust=0.5, hjust=1.00, position = position_dodge(width = 1), color="pink", size = 5)+
  xlab("Candy Name")+ggtitle("Top Five Candies with 'MEH' by Girls")+
  scale_fill_gradient(low = 'palevioletred4', high = 'palevioletred')

plot2=ggplot(arrange(filter(candy1, gender == 'Male'),desc(MEH))[1:5,], aes(x=reorder(candy_name, MEH), y = MEH, fill = MEH))+
  geom_bar(stat = 'identity')+
  coord_flip()+
  geom_text(aes(label=MEH),vjust=0.5, hjust=1.00, position = position_dodge(width = 1), color="pink",size = 5)+
  xlab("Candy Name")+ggtitle("Top Five Candies with 'MEH' by Guys")
ggarrange(plot1,plot2,nrow=2)
```

# DATASET 2   
Importing Data from Github
```{r}
Testscores_df <- read_csv('https://raw.githubusercontent.com/Meccamarshall/Data607/main/Project%202/testscores.csv', 
                          show_col_types = FALSE)
```

### Creating a dataframe
```{r}
Testscores_df <- data.frame(Testscores_df)
Testscores_df %>% 
head(10) %>%
  kable() %>% 
  kable_styling(bootstrap_options = "striped", font_size = 12, fixed_thead = T) %>%  scroll_box(height = "300px", width = "100%")
```

### Tidying the Student Test Score Results data
```{r}
colnames(Testscores_df) <- c("StudentID","Gender", "EthnicGroup", "ParentEduc", "LunchType", "TestPrep", "MathScore", "ReadingScore", "WritingScore")
colnames(Testscores_df) <- c("StudentID","Gender", "EthnicGroup", "ParentEduc", "LunchType", "TestPrep", "MathScore", "ReadingScore", "WritingScore")
Testscores_df%>% 
head(10) %>%
  kable() %>% 
  kable_styling(bootstrap_options = "striped", font_size = 12, fixed_thead = T) %>%  scroll_box(height = "300px", width = "100%")
```

# DATASET 3 - Subway Riders Annually
### Load data from github

```{r}
url <- 'https://raw.githubusercontent.com/Meccamarshall/Data607/main/Project%202/2022%20Subway%20Tables_ul.csv'

MTA_df <- read.csv(file = url)

na.omit(MTA_df)

str(MTA_df)
```

### Cleaning and Tidying up the dataset
```{r}
# Creating new column names
newcolumn <- c('Station', 2017, 2018, 2019, 2020, 2021, 2022, '2021 - 2022 Net Change', 
                   '2021 - 2022 % Change', '2022 Rank')
colnames(MTA_df) <- newcolumn

# Finding borough rows
borough <- c('The Bronx', 'Brooklyn', 'Manhattan', 'Queens')

rowvalues <- c()

for(i in 1:length(borough)){
  rowvalues[i] <- rownames(MTA_df[which(MTA_df$'2017' == borough[i]),])
}
rowvalues
```

### Analyzing and creating visuals for the data
```{r}
dfBronx <- MTA_df[2:69,]
dfBronx['Borough'] <- borough[1]
  
dfBrooklyn <- MTA_df[71:227,]
dfBrooklyn['Borough'] <- borough[2]

dfManhattan <- MTA_df[229:349,]
dfManhattan['Borough'] <- borough[3]

dfQueens <- MTA_df[351:dim(MTA_df)[1],]
dfQueens['Borough'] <- borough[4]

MTA_df2 <- rbind(dfBronx, dfBrooklyn, dfManhattan, dfQueens)

# Removing commas and transforming characters into integers
MTA_df2 <- MTA_df2 %>%
  mutate(x = droplevels(MTA_df2),
         '2017' = as.integer(str_remove_all(MTA_df2$'2017', ',')),
         '2018' = as.integer(str_remove_all(MTA_df2$'2018', ',')),
         '2019' = as.integer(str_remove_all(MTA_df2$'2019', ',')),
         '2020' = as.integer(str_remove_all(MTA_df2$'2020', ',')),
         '2021' = as.integer(str_remove_all(MTA_df2$'2021', ',')),
         '2022' = as.integer(str_remove_all(MTA_df2$'2022', ',')),
         '2021 - 2022 Net Change' = as.integer(str_remove_all(MTA_df2$'2021 - 2022 Net Change', ',')),
         '2021 - 2022 % Change' = as.numeric(str_remove_all(MTA_df2$'2021 - 2022 % Change', '%')),
         '2022 Rank' = as.integer(MTA_df2$'2022 Rank')) %>% 
select(Borough, colnames(MTA_df2))
```


```{r}
colnames2 <- c('Borough', 2017, 2018, 2019, 2020, 2021, 2022)

MTA_df3 <- MTA_df2  %>%
  select(colnames2)
```

```{r}
avgMTA <- MTA_df3 %>%
  pivot_longer(!Borough, names_to = 'Year', values_to = 'Ridership') %>%
  group_by(Borough, Year) %>%
  summarize(Avg_Ridership = mean(Ridership, na.rm = TRUE))
```

```{r}
ggplot(data = avgMTA) +
  geom_bar(mapping = aes(x = Year, y = Avg_Ridership, fill = Borough), stat = 'identity') +
  facet_grid(~ Borough) +
  theme(axis.text.x = element_text(angle = 70, hjust = 1)) +
  labs(title = 'Average Riderhip from 2017 - 2022 by Borough')
```