---
title: "Data 607 - Week 3 R Character Manipulation and Date Processing"
author: "Shamecca Marshall"
date: "2023-08-31"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

## 1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r include=FALSE, results='hide'}
library(tidyverse)
library(openintro)
library(conflicted)
library(dplyr)
```
# Load data from GitHub
```{r echo=TRUE}
majors = read.csv(file="https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv", header= TRUE,sep=",")
str(majors)
```

# Provide code that identifies the majors that contain either "DATA" or "STATISTICS"
```{r echo=TRUE, results='hide'}
grep(pattern = 'data|statistics',majors$Major, value = TRUE, ignore.case = TRUE)
```

## 2. Write code that transforms the data below:
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"
Into a format like this:
c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")
```{r}
fruits_raw = '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"'


fruits_clean = c(scan(text=fruits_raw, what="character", quiet=TRUE))
fruits_clean = Filter(function(x) !any(grepl("\\[", x)), fruits_clean)
fruits_clean
```

## 3. Describe, in words, what these expressions will match:
(.)\1\1 - Matches string with the same character repeated three times ex. 1215-2999 it will match 999


(..)\1 - Matches string format that has two characters repeated twice in the same order ex. 211414 it will match 1414

"(.).\\1.\\1" - Matches a character with the first character followed by the first character, followed by any other character, followed by the first character e.g. in string ex. 212329549 will match 21232

"(.)(.)(.).*\\3\\2\\1" - Matches three characters that are following by zero or more characters and then have the pattern in reverse order. ex 214feb1994pink1215 it will match feb1994pink



### 4. Construct regular expressions to match words that:
# Start and end with the same character.
```{r}
s<- c("tweet", "tomorrow", "Mississippi", "appropriate", "educate", "dazed", "eleven", "error", "nanny", "church")
```

```{r}
str_view(s, "^(.)((.*\\1$)|\\1$)")
```
# Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r}
str_view(s, "([A-Za-z][A-Za-z]).*\\1")
```

# Contain one letter repeated in at least three places (e.g. “eleven” contains three “e”s.)
```{r}
str_view(s, "([A-Za-z]).*\\1.*\\1")
```