---
title: "Working with Tidy Data"
author: "Shamecca Marshall"
date: "2023-10-01"
output:
  pdf_document: default
  html_document: default
---

## Data gathering, tidying and transformation
```{r, results = "hide"}
rm(list = ls())
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(reshape2)
library(tidyselect)
```

## Loading Data into R
```{r}
data<- read.csv("https://raw.githubusercontent.com/Meccamarshall/Data607/main/flight%20status%20data%20607.csv", sep = ",", header = TRUE)
data
```

## Removing the NA’s
Since there is a row with NA, I want remove that from my data set.
```{r}
data<-drop_na(data,)
data
```

```{r}
data$Airline[data$Airline==""]<-c("Alaska","AM West")
data
```

## Transform data from wide format to long format
Since I need to compare the delayed time, I reformatted this to the long way that way it would be easier for me to view the dataset
```{r}
data1<- data %>% gather(key = Destination, value= Count, c(3:7))
```

```{r}
data1
```
## Filtering by delays
Since I am only interested in viewing the delays, I am hiding the on time data from the data frame.
```{r}
data2<-filter(data1, Delay.Status=="delayed")
```

```{r}
data2
```
## Comparisons
```{r}
data2$Count = as.numeric(as.character(data2$Count))
data2
```

```{r}
summary(data2$Count)
```

```{r}
summarise(data2, mean=mean(Count), sd=sd(Count))
```
From this given data set, it can be seen that that there is an average of 129 flight delays with a standard deviation of approximately 130.

```{r}
barplot(data2$Count)
```

## Viewing Alaska delays
```{r}
library(ggplot2)
Alaska_delays<-filter(data2, Airline=="Alaska")
Alaska_delays
```

```{r}
ggplot(Alaska_delays,aes(Destination,Count)) +
geom_bar(aes(fill = Airline), position = "dodge", stat = "identity", col = "red") + 
  ylab("Count")
```

## Viewing AM West delays
```{r}
library(ggplot2)
AM_West_delays<-filter(data2, Airline=="AM West")
AM_West_delays
```

```{r}
ggplot(AM_West_delays,aes(Destination,Count)) +
geom_bar(aes(fill = Airline), position = "dodge", stat = "identity", col = "red") + 
  ylab("Count")
```
  
##Conclusion

After carefully analysizing the data in the dataset used in this assignment, Alaska airlines seems to be a more reliable airline with minimal flight delays, compared to AM West airlines.