---
title: "Project 1"
author: "Shamecca Marshall"
date: "2023-09-22"
output:
  html_document: default
  pdf_document: default
---

## Loading and reading the data
```{r}
library(stringr)
library(readr)
url = 'https://raw.githubusercontent.com/Meccamarshall/Data607/main/tournamentinfo.txt'
chesstournament = readLines(url)
```

```{r}
head(chesstournament)
```

```{r}
tail(chesstournament)
```

## Deconstructing the Data
### After noticing that the first four lines were not apart of the dataset, I decided that it needed to be deconstructed. The first four lines are followed by player info and the games played and then repeated. I am going to seperate the data into two matrices to show a cleaner dataset.
```{r}
cTournament <- matrix(unlist(chesstournament), byrow=TRUE)

c1 <- cTournament[seq(5,length(cTournament),3)]
head(c1)
```

```{r}
c2 <- cTournament[seq(6,length(cTournament),3)]
head(c2)
```

## Capturing the data
### I need to capture the values in vectors using regular expressions and string manipulation.
```{r}
# matching first numbers
ID <- as.numeric(str_extract(c1, '\\d+'))

# matching the first combination of a letter, any amount of characters and "|"
Name <- str_extract(c1, '[A-z].{1,32}') 

# extracting the name
Name <- str_trim(str_extract(Name, '.+\\s{2,}'))

# matching the first two letters (state) in the second matrix 
State <- str_extract(c2, '[A-Z]{2}') 

# matching at least 1 number, a period, and 1 number
TotalNumberofPoints <- as.numeric(str_extract(c1, '\\d+\\.\\d'))

# matching the combination of "R", any characters and "-"
PreRating <- str_extract(c2, 'R:.{8,}-')

# matching first 4 numbers
PreRating <- as.numeric(str_extract(PreRating, '\\d{1,4}'))

# matching all combinations of 1 letter 2 spaces and any numbers
Rounds <- str_extract_all(c1, '[A-Z]\\s{2,}\\d+')

# matching numbers
Rounds <- str_extract_all(Rounds, '\\d+')
```
## Calculating Average Pre Chess Rating of Opponents
```{r}
AvgOppPreChessRating <- c()

for(i in c(1:length(Rounds))){
  AvgOppPreChessRating[i] <- round(mean(PreRating[as.numeric(Rounds[[i]])]),0)
}
AvgOppPreChessRating
```
## Constructing the data frame
```{r}
Project1 <- data.frame(ID,Name,State,TotalNumberofPoints,PreRating,AvgOppPreChessRating)

head(Project1)
```
## Writing the CVS file
```{r}
write_csv(Project1, 'ChessTournament.csv' , append = FALSE)
```
