---
title: "Data 607 - Assignment 9"
author: "Shamecca Marshall"
date: "2023-11-05"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Assignment - Web APIs
The New York Times web site provides a rich set of APIs, as described here: [https://developer.nytimes.com/apis]( https://developer.nytimes.com/apis) You’ll need to start by signing up for an API key. Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.

# Libraries 
```{r}
# load libraries
library("httr")
library("jsonlite")
library("dplyr")
library("kableExtra")
library("stringr")
library("ggplot2")
library("tidyverse")
```

# Connecting API
I will be using the Top stories API, filtered for the following section:
- Fashion

Let’s first read in the data from the API:
```{r}
# API Key
apikey <- "Jb1d6yqzl4VulbGuWbH0BbCMSPjfowxg"

# Get the URL 
theURL <- paste("https://api.nytimes.com/svc/topstories/v2/fashion.json?api-key=", apikey)

fashionstories <- GET(theURL)

# Get status code
fashionstories$status_code
```

```{r}
summary(fashionstories)
```

```{r}
fashion_stories <- content(fashionstories, as = "text")
```

Data Frame Conversion
```{r}
fashion_stories2 <- fromJSON(fashion_stories, flatten = TRUE)
fashion_stories2 <- data.frame(fashion_stories2$results, stringsAsFactors = FALSE)

#Get column names
colnames(fashion_stories2)
```

```{r}
#Rename columns
colnames(fashion_stories2) <- c("Section","Subsection", "Title", "Abstract", "URL", "URI", "Byline", "Item_Type", "Updated_Date", "Created_Date", "Published_Date", "Material_Type_Facet", "Kicker", "Des_Facet", "Org_Facet", "Per_Facet", "Geo_Facet", "Multimedia", "Short_Url")

#Drop columns not needed
fashion_stories3 <- fashion_stories2[, -c(12:18)]
```

# Data Analysis
```{r}
#Count of Section
Section <- fashion_stories3%>%
  group_by(Section)%>%
  summarise(num=n())%>%
  arrange(desc(num))
head(Section)
```

```{r}
#Count of Subsection
Subsection <- fashion_stories3%>%
  group_by(Subsection)%>%
  summarise(num=n())%>%
  arrange(desc(num))
head(Subsection)
```

# Plots
The bar plot below shows that plenty of the articles belong to the fashion section followed by style and t-magazine.
```{r}
# Bar Plot for Section
fashion_stories3 %>% 
ggplot(aes(x = Section)) +
  geom_bar(fill = "hotpink")
```
Within the next bar plot there is an unknown subsection that has the highest count followed by Africa and design.
```{r}
# Bar Plot for Subsection
fashion_stories3 %>% 
ggplot(aes(x = Subsection)) +
  geom_bar(fill = "hotpink4")
```