---
title: "Data 607 - Week 10"
author: "Shamecca Marshall"
date: "2023-11-13"
output:
  html_document:
    includes:
      in_header: header.html
    css: ./lab.css
    highlight: pygments
    theme: cerulean
    toc: true
    toc_float: true
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

**Assignment**
In Text Mining with R, Chapter 2 looks at Sentiment Analysis. In this assignment, you should start by getting the primary example code from chapter 2 working in an R Markdown document. You should provide a citation to this base code. You’re then asked to extend the code in two ways:

Work with a different corpus of your choosing, and
Incorporate at least one additional sentiment lexicon (possibly from another R package that you’ve found through research).

**Loading Libraries**
```{r}
library(tidytext)
library(textdata) 
library(janeaustenr)
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(tidyverse)
library(wordcloud)
library(reshape2)
library(harrypotter)
library(RCurl)
```

**Jane Austen Dataset**
```{r}
# get linenumber and chapter 
tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, 
                                     regex("^chapter [\\divxlc]", 
                                                 ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)


nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)
```

```{r}
jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)



ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")
```

```{r}
# compairing 3 sentiment dictionaries
pride_prejudice <- tidy_books %>% 
  filter(book == "Pride & Prejudice")

pride_prejudice
```

```{r}
afinn <- pride_prejudice %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")

bing_and_nrc <- bind_rows(pride_prejudice %>% 
                            inner_join(get_sentiments("bing")) %>%
                            mutate(method = "Bing et al."),
                          pride_prejudice %>% 
                            inner_join(get_sentiments("nrc") %>% 
                                         filter(sentiment %in% c("positive", 
                                                                 "negative"))) %>%
                            mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)

get_sentiments("nrc") %>% 
     filter(sentiment %in% c("positive", 
                             "negative")) %>% 
  count(sentiment)
```

```{r}
get_sentiments("bing") %>% 
  count(sentiment)
```

```{r}
# most common positive and negative words
bing_word_counts <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts
```

```{r}
bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(
    y = "Contribution to sentiment",
    x = NULL
  ) +
  coord_flip()
```

```{r}
custom_stop_words <- bind_rows(tibble(word = c("miss"), 
                                          lexicon = c("custom")), 
                               stop_words)

custom_stop_words
```

```{r}
# wordclouds
tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```

**New Corpus**
	
Alice's Adventures in Wonderland is a children's literature book written by Lewis Carroll.

```{r}
library(gutenbergr)
gutenberg_metadata
```

**Convert Data to Tidy**

```{r}
count_of_Alice_Wonderland<- gutenberg_download(11) 
count_of_Alice_Wonderland
```
**Using lexicon to perfom sentiment analysis**
```{r}
Alice_Wonderland_Chapters <- count_of_Alice_Wonderland %>% 
  filter(text != "") %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("CHAPTER [\\dIVXLC]", ignore_case =  TRUE)))) 

Alice_Wonderland_Chapters
```

```{r}
Alice_Wonderland_tidy <- Alice_Wonderland_Chapters %>% 
  unnest_tokens(word, text) %>% 
  inner_join(get_sentiments("loughran")) %>% 
  count(word, sentiment, sort = TRUE) %>%
  group_by(sentiment) %>%
  top_n(10) %>% ungroup() %>% mutate(word = reorder(word, n)) %>%
  anti_join(stop_words)

names(Alice_Wonderland_tidy)<-c("word", "sentiment", "Freq")

ggplot(data = Alice_Wonderland_tidy, aes(x = word, y = Freq, fill = sentiment)) + 
  geom_bar(stat = "identity") + coord_flip() + facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",x = NULL) 
```

**Frequent used positive and negative words**
The most frequent used words for positive sentiments and negative sentiments.
```{r}
Alice_Wonderland_Sentiment_total <- Alice_Wonderland_Chapters %>%
  unnest_tokens(word, text) %>% inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

Alice_Wonderland_Sentiment_total %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip() +
  geom_text(aes(label = n, hjust = 1.0))
```

**Chapter wise positive and negative words*
```{r}
Alice_Wonderland_Sentiment <- Alice_Wonderland_Chapters %>%
  unnest_tokens(word, text) %>%
  inner_join(get_sentiments("bing")) %>%
  count(chapter, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)

ggplot(Alice_Wonderland_Sentiment, aes(index, sentiment, fill = chapter)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~chapter, ncol = 2, scales = "free_x")
```

```{r}
Positive_Negative_Count<- Alice_Wonderland_Chapters %>% 
   unnest_tokens(word, text) %>%
  inner_join(get_sentiments("afinn")) %>%
  group_by(index = linenumber %/% 80, chapter)%>%
  summarise(sentiment = sum(value))

Positive_Negative_Count%>%
  ggplot(aes(chapter, sentiment, fill=index)) +
  geom_col()
```

**Wordcloud**
The most common words in "Alice's Adventures in Wonderland."
```{r}
total_word_count <- Alice_Wonderland_Chapters %>% unnest_tokens(word, text) %>% 
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>% filter(word != "" )

total_word_count %>% with(wordcloud(word, n, max.words = 100))
```